Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-03-01 manuscript/cpcrw_manuscript.Rmd
Bumping up flux values to ensure all positive numbers
Following Treat et al. (2015). Do we want to transform CH4 fluxes to ng?

The effects of temperature, gravimetric water content, C percent, N percent, and DOC concentration on instantaneous gas fluxes were evaluated using a linear mixed-effects model fit by the R function *lme* in the R 'nlme' package, , version `r packageVersion("nlme")`. Because the dependent variable (CO~2~ or CH~4~ flux) was non-normally distributed, it was transformed using a natural-logarithm transformation. Core number was treated as a random effect in the model. We then used performed stepwise model selection by Akaike's information criterion (AIC) using the *stepAIC* function in the R 'MASS' package, version `r packageVersion("MASS")`. A linear mixed-effects model was also used to evaluate the effect of treatment on core water content. The effect of temperature and treatment (drought, controlled drought, or field moisture conditions) on cumulative gas fluxes was evaluted with a post-hoc Tukey Honest Significant Differences test.

@@

**Table 1.** Statistical tests of WC, T, C, N on individual core CO2 fluxes.

@@

**Table 2.** Statistical tests of WC, T, C, N on individual core CH4 fluxes.

>>>>

The effects of temperature, gravimetric water content, C percent, N percent, and DOC concentration on instantaneous gas fluxes were evaluated using a linear mixed-effects model fit by the R function *lme* in the R 'nlme' package, , version `r packageVersion("nlme")`. Because the dependent variable (CO~2~ or CH~4~ flux) was non-normally distributed, it was transformed using a natural-logarithm (+`r FLUX_ADDITION` µg C g C^-1^ day^-1^ to ensure all positive fluxes) transformation. Core number was treated as a random effect in the model. We then used performed stepwise model selection by Akaike's information criterion (AIC) using the *stepAIC* function in the R 'MASS' package, version `r packageVersion("MASS")`. A linear mixed-effects model was also used to evaluate the effect of treatment on core water content. The effect of temperature and treatment (drought, controlled drought, or field moisture conditions) on cumulative gas fluxes was evaluted with a post-hoc Tukey Honest Significant Differences test.

@@

**Table 1.** Linear mixed-effects model parameters, testing effects of gravimetric water content (unitless), temperature (°C), soil C (%), soil N (%),  and dissolved organic carbon (mg kg^-1^) on individual core CO~2~ fluxes (+`r FLUX_ADDITION` µg C g C^-1^ day^-1^). Dependent variable has units of log(µg C g C^-1^ day^-1^). Columns include parameter value; standard error (SE); degrees of freedom (DF); T statistic; and P value.

@@

**Table 2.** Linear mixed-effects model parameters, testing effects of gravimetric water content (unitless), temperature (°C), soil C (%), soil N (%),  and dissolved organic carbon (mg kg^-1^) on log-transformed, individual core CH~4~ fluxes (+`r FLUX_ADDITION` µg C g C^-1^ day^-1^). Dependent variable has units of log(µg C g C^-1^ day^-1^). Columns include parameter value; standard error (SE); degrees of freedom (DF); T statistic; and P value.
